---
output:
    github_document
editor_options:
    chunk_output_type:
        console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lego

The goal of lego is to make it possible for lego-lovers to prototype builds _in silico_.

## Installation

`lego` is not yet on CRAN, so for now you can download it from github with:

```{r eval=FALSE}
install.packages('devtools')
devtools::install_github(repo = 'rcorty/lego')
```

## Setup

To run any of the examples below, you'll need to start by loading `lego` and `dplyr`.

```{r eval=FALSE}
library(dplyr)
library(lego)
```

## Example 1

I want to stack a 2x2 brick on top of a 4x2 brick.
It's easy!

```{r eval=FALSE}
new_build() %>% 
    lay_brick(width = 4, depth = 2) %>% 
    lay_brick_square(size = 2) ->
    build1

build1
```

You might say this build isn't much, but it's a valid build, as we can verify with:

```{r eval=FALSE}
check_build(build = build1)
```

Great -- let's have a look:

```{r eval=FALSE}
render_image(build = build1)
```

And now let's have a look in 3D ðŸ˜

```{r eval=FALSE}
render_3D(build = build1)
```

## Example 2

They way I made `build1` took advantage of a lot of "syntactic sugar", allowing the code to be very short.
Now, let's make the same `build` more explicitly.

```{r eval=FALSE}
new_build(
    space = new_space(
        width = 10,
        height = 10,
        depth = 10
    ),
    blocks = new_blockset(
        name = 'classic_bucket'
    )
) %>% 
    lay_block(
        block = new_block(
            type = 'brick',
            width = 4, 
            depth = 2
        ),
        where = c(x = 0, y = 0)
    ) %>% 
    lay_block(
        block = new_block(
            type = 'brick',
            width = 2, 
            depth = 2
        ),
        where = c(x = 0, y = 0)
    ) ->
    build2

build2
```

That was a much longer way to build (what appears to be) the same thing.
Let's confirm that they are actually the same.:

```{r eval=FALSE}
identical(build1, build2)
```

If we render an image and/or a 3D image of `build2`, it will be the same as `build1`.
So let's move on to a more complex example.

## Example 3

Let's lay some more blocks of different types in different places.

Some examples that work.

[do it here]

Now some that generate warning messages.

[do it here]

See, we can change the options to not hassle us about builds that have various faults.
Let's say I don't want to hear about using blocks that aren't in my blockset or placing blocks unsupported.

[do it here]

Now we can rerun that code that gave those warnings.

[do it here]

Great...no warnings.
But, we didn't actually fix anything.

When we `check_build`, of course we get those warnings back.

[do it here]

So how can we really address them?
Well, for a warning about using a block that's not in the blockset, we can just add to the blockset.

[do it here]

Remember, we're all digital at this point, so blocks are free.
You may want to go on [Pick-A-Brick](https://shop.lego.com/en-US/Pick-a-Brick) or [bricklink](https://www.bricklink.com/v2/main.page) to figure out how to get the blocks you need for a price you can afford.
`lego` will output a list of blocks you ended up using, which should be helpful.

To address the warning about unsupported `block`s, we can simply unlay the unsupported blocks and view the `build` again to see if we're happy without them.

[do it here]

If we're not happy without those `blocks` laid, we'll have to re-design.

[do it here]


## Example 4

Now I want to build a house.
I can make a simple house with:

```{r eval=FALSE}
new_build() %>% 
    lay_tube(
        cross_section = lego_rectangle(
            width = 4,
            depth = 4
        ),
        extent = 4,
        where = c(x = 3, y = 3, z = 0)
    ) %>% 
    lay_panel(
        corner1 = c(x = 3, y = 3, z = 5),
        corner2 = c(x = 7, y = 5, z = 7)
    ) %>% 
    lay_panel(
        corner1 = c(x = 3, y = 5, z = 7),
        corner2 = c(x = 7, y = 7, z = 5)
    ) ->
    build3

build3
```

Now we can have a look at our simple house:

```{r eval=FALSE}
render_image(build = build3)
```

...and in 3D...

```{r eval=FALSE}
render_3D(build = build3)
```


## Example 5

Add features to `tube` like windows?
Save a point in space based on being a corner of one layer, then refer to it in future layers?

Specify a unit and a symmetry to make a tesselation or something?

## Colors

This package uses the colors from `legocolors`.  The most commonly used colors are the first 8 in the "solid" palette:

```{r echo = FALSE, fig.height=3}
par(bg = 'lightgray', mar = c(4, 2, 4, 2))
plot(x = 1:8, y = rep(0, 8), col = legocolors::legopals$solid[1:8], pch = 15, cex = 6, axes = FALSE, xlab = NA, ylab = NA, main = 'The first 8 colors of the "solid" palette')
```

The entire "solid" palette contains these 80 colors:

```{r echo = FALSE, fig.height=6}
par(bg = 'lightgray', mar = c(4, 2, 4, 2))
plot(x = rep(x = 1:9, each = 9), y = rep(x = 1:9, times = 9), col = c(legocolors::legopals$solid, NA), pch = 15, cex = 6, axes = FALSE, xlab = NA, ylab = NA, main = 'The 80 colors of the "solid" palette')
```

